Synthesizing Symmetric Lenses: Artifact Evaluation

### 2019-05-29 papers/SymmetricLenses/ArtifactEvaluationPaper/main.tex
more updates

\title{Synthesizing Bijective Lenses: Artifact Evaluation}

@@

@@

% begin introduction
\section{Setup Environment}
\subsection{Virtual Machine Environment (recommended)}
To make validation easier, we provide the Artifact Evaluation Committee with a
virtual machine that has all components installed.  Setup for the virtual
machine environment detailed below:
\begin{enumerate}
\item Install a Virtual Machine Manager (we tested with VirtualBox)
\item Download our virtual machine image (BijectiveLensSynthesis.ova in\\
  {\color{blue}
    \url{https://drive.google.com/drive/folders/0B5OYxhNvX675cTN4ZzVEMmJ0Mlk})}
\item Load our virtual machine from your virtual machine manager
\end{enumerate}

We suggest the committe dedicate over 8GB RAM to this environment.
While we get similar results with less RAM, some of the existing tools we
compare our artifact to use up to 8GB RAM.  Less RAM may cause these tools to
perform worse than presented in our data.

The user for the virtual machine is bls, with password bls.

\subsection{Custom Environment}
If you want to install on a custom environment, certain programs and libraries
must be installed.  We provide the commands for installation in Ubuntu 16.04.3
in parenthesis next to the program or library name.

\begin{enumerate}
\item Install opam (sudo apt install opam; opam init; eval `opam config env`;
  opam update)
\item Switch opam to OCaml 4.03.0 (opam switch 4.03.0; eval `opam config env`)
\item Install necessary system packages (opam depext conf-m4.1)
\item Install OCaml's Core (opam install core)
\item Install OCaml's Menhir (opam install menhir)
\item Install OCaml's OUnit (opam install ounit)
\item Install OCaml's ppx\_deriving (opam install ppx\_deriving)

\item Install python-pip (sudo apt install python-pip)
\item Install Python's EasyProcess (pip install EasyProcess)
\item Install Python's matplotlib (pip install matplotlib)
\item Install Python's tk (sudo apt install python-tk)

\item Install DotNet runtime environment, and C\# and Visual Basic libraries and
  compilers (sudo apt install mono-complete; sudo apt install mono-vbnc)

\item Install the codebase\\
  (git clone https://github.com/Miltnoid/BijectiveLensSynthArtifactEvaluation.git)
\end{enumerate}

@@

To validate: navigate to the directory the codebase is installed in
(/home/bls/LensSynth in the virtual machine).
Then run the following commands:
\begin{enumerate}
\item make regenerate-specs
\item make regenerate-data
\end{enumerate}

After these commands are run, the figures will be present at the following
locations: 
\begin{itemize}
\item Figure 8 will be present at \$/generated-graphs/times.eps
\item Figure 9 will be present at \$/generated-graphs/uninferred.eps
\item Figure 10 will be present at \$/generated-graphs/compositional.eps
\item Figure 11 will be present at \$/generated-graphs/examples.eps
\end{itemize}

The command ''make regenerate-specs`` will take about an hour to complete.  It
must run to completion for the data to be saved.

@@

The command, ``make regenerate-data'' can be stopped when partially completed.
After a benchmark has had all tests run on it, that data is saved, so future
runs will not rerun tests on that benchmark.  Each benchmark takes between 0 and
3 hours to complete, with information being printed to stdout about what
test and benchmark is being run.  The total time to complete all tests takes
between 2 and 3 days.

@@

If the artifact committee want to do more in-depth testing, we provide
information on the individual project directories.  The means to run individual
programs are described in README.txt files in the directories.

\paragraph*{\$/program}  Our tool is present in the program directory.  The
source code is provided in \$/program/src .  The directory \$/program/tests
contains a test suite, consisting of microbenchmarks and the tested benchmarks.
The directory \$/program/example-inputs contains the tested benchmarks.
The directory \$/program/generated\_data is the output location for the csv created from
program runs.  The directories \$/program/generated\_extraction\_specs and
\$/program/generated\_io\_specs are the output locations for the specifications
given to Flash Fill and FlashExtract.

\paragraph*{\$/comparisons}  When created by ``make regenerate-specs'', the
directories \$/comparisons/extraction\_specs and \$/comparisons/io\_specs
contain the specifications given to Flash Fill and FlashExtract.  The directory
\$/comparisons/prose/Transformation.Text contains the generated data for its
runs under generated\_data, and the source code for our tests in
SampleProgram.cs.  The directory
\$/comparisons/prose/Extraction.Text contains the generated data for its
runs under generated\_data, and the source code for our tests in
LearningSamples.cs.

>>>>

\title{Synthesizing Symmetric Lenses: Artifact Evaluation}

@@

\author{Solomon Maina}
\affiliation{University of Pennsylvania, USA}
\email{smaina@seas.upenn.edu}

@@

% begin introduction
\section{Setup Environment}
\subsection{Virtual Machine Environment (recommended)}
To make validation easier, we provide the Artifact Evaluation Committee with a
virtual machine that has all components installed.  Setup for the virtual
machine environment detailed below:
\begin{enumerate}
\item Install a Virtual Machine Manager (we tested with VirtualBox)
\item Download our virtual machine image (SymmetricLensSynthesis.ova in\\
  {\color{blue}
    \url{https://drive.google.com/drive/folders/1en7-K6Kxp7MvF3Z1GGfpCDBIKuF-84YM})}
\item Load our virtual machine from your virtual machine manager
\end{enumerate}

We suggest the committe dedicate at least 8GB RAM to this environment.

The user for the virtual machine is ae, with password 2019.

\subsection{Custom Environment}
If you want to install on a custom environment, certain programs and libraries
must be installed.  We provide the commands for installation in Ubuntu 16.04.6
in parenthesis next to the program or library name.

\begin{enumerate}
\item Install opam (sudo apt install opam; opam init; eval `opam config env`;
  opam update)
\item Install necessary system packages (opam depext conf-m4.1)
\item Install OCaml's JBuilder (opam install jbuilder)
\item Install OCaml's Core (opam install core)
\item Install OCaml's Menhir (opam install menhir)
\item Install OCaml's OUnit (opam install ounit)
\item Install OCaml's ppx\_deriving (opam install ppx\_deriving)
\item Install OCaml's ppx\_hash (opam install ppx\_hash)

\item Install python-pip (sudo apt install python-pip)
\item Install Python's EasyProcess (pip install EasyProcess)
\item Install Python's matplotlib (pip install matplotlib)
\item Install Python's tk (sudo apt install python-tk)
\item Install Python's numpy (sudo apt install numpy)

\item Download the codebase\\
  (git clone https://github.com/Miltnoid/SymmetricLensSynthArtifactEval.git)
\end{enumerate}

@@

To validate: navigate to the directory the codebase is installed in
(/home/ae/SymmetricLensSynthArtifactEval in the virtual machine).
Then run the following command: ``make regenerate-data''

After this command is run, the figures will be present at the following
locations: 
\begin{itemize}
\item Figure 6 will be present at \$/generated-graphs/times.eps
\item Figure 7 will be present at \$/generated-graphs/times\_bijective.eps
\item Figure 8 will be present at \$/generated-graphs/metrics\_importance.eps
\end{itemize}

The command ``make regenerate-data'' will take a few hours to complete. It
must run to completion for the data to be saved.

@@

@@

If the artifact committee want to do more in-depth testing, we provide
information on the individual project directories. Boomerang can be built by
running ``make'' in the \$/boomerang directory, and run with ./boomerang.exe.

\paragraph*{\$/boomerang} Boomerang enhanced with symmetric lenses is present in
the program directory. The optician source code is provided in
\$/boomerang/optician . The directory \$/program/examples contains example
boomerang programs, and the directory \$/program/examples/synth\_examples
contains examples using synthesis.
